One Year HPC Certification Forum in Retrospective

### 2019-04-16 paper.tex
Kays comments.

\newcommand{\jk}[1]{\todo[inline]{TODO: #1}}
\newcommand{\ag}[1]{\todo[inline]{IDEA: #1}}

@@

The article is structured as follows:
First, we introduce the HPC Certification Forum and the program in \Cref{sec:forum}.
Then, an overview of the status is given in \Cref{sec:status}.
Next, the organization of competences is discussed in \Cref{sec:skills}.
This leads to the prototypical approach for the certification process in \Cref{sec:certification}.
In \Cref{sec:ecosystem} there the ecosystem is described.
Related work is presented in \Cref{sec:related}.
Finally, the article is concluded in \Cref{sec:conclusion}.

@@

The forum is organized using a Webpage\footnote{http://hpc-certification.org} and utilizes Slack for communication and monthly meetings.
Members are organized in different roles:
Anyone can become an associate member in the HPCCF free of charge -- e.g., observing the status, being listed on the webpage.
Full members must actively contribute to the program to some extent and have voting rights for the roles of the steering board.
The steering board directs the overall activities and is organized in different responsibilities, i.e., into topic-specific chairs.

@@

\paragraph{Management}
At ISC-HPC 2018, the first steering board had been elected.
We established communication channels via webpage, email and Slack for regular discussion.
Slack is also used to conduct our monthly open meetings between members and the steering board.
At beginning we used video conferencing tools, but found that the chat provides a more inclusive discussion and the asynchronous nature is more productive.
We also established relations with various stackholders involved in HPC education growing the participation in the forum.
Meeting notes with action items are extracted from Slack and documented using Google Doc.

Note that until now contributions of members are voluntarily and follow the schedule as agreed between the contributor and the HPCCF board.
We manage the prospect contributions in a Trello board; each member can manage its own card.

\paragraph{Technical}
According to our goals, we address 1) the definition of competences; 2) the creation of certificates; 3) the examination of practitioners; and 4) an ecosystem of tools supporting them.

@@

A skill is defined as a set of competences (learning outcomes) and some metadata.
This model can be compared to the classification of school knowledge, for example, the skill with the short name “addition” could describe the math skill of being able to add numbers successfully.
Within a single skill, there can also be multiple levels (basic, intermediate, expert level) building upon each other that distinguish the expertise further.
We expect that practitioners acquire the lower levels before progressing to more complex levels.
In our addition example, \textit{basic level}, for example, may mean to be able to add two positive numbers while the \textit{expert level} of that skill could indicate to be able to add multiple numbers.

@@

On the leaf level, a skill is fine-grained and orthogonal to other skills -- we scope the level of detail here to be able to be taught in a 1.5 hour lecture up to a 4 hour workshop.
We believe this is a good granularity as it allows practitioners to cherry-pick the relevant skills and lecturers and examiners to prepare small lectures with well-defined content.
\ag{change sentence because provided that provide - \\
Instead: For technology-dependent skills on leaf level (e.g., a specific file system or workload manager), often introductory skills are provided that provide the foundation to many specialized skills each representing a specific hardware or software technology.\\
write it this way: For technology-dependent skills on leaf level (e.g., a specific file system or workload manager), often introductory skills are provided that contribute to the foundation of many specialized skills each representing a specific hardware or software technology.
}
The aggregation within the tree is similar to the aggregation found in education as part of “individual teaching events”, “those specified for modules or short courses”, and “those specified for whole degree programmes” \cite{hussey2008learning}.
While that Hussey et al. conclude that LOs on the coarse grained level are not useful for high-level education, we use a similar concept, but relax the granularity/abstraction level of the learning outcome.

@@

The following skill describes a leaf-level skill for the usage of SLURM in the basic level.
While there is no formal dependency to the introduction (skill USE4.2.2-B), it is expected that practitioners have obtained the other skill before learning this one.

\begin{itemize}
  \item \textbf{ID}: USE4.2.2-B
  \item \textbf{Name}: SLURM Workload manager
  \item \textbf{Background}: SLURM is a widely used open-source workload manager providing various advanced features.
  \item \textbf{Aims}:
  \begin{itemize}
    \item To enable practitioners to use relevant tools to run and monitor parallel applications using SLURM.
    \item To enable practitioners to comprehend and describe the basic architecture of SLURM and the suite of tools.
  \end{itemize}
  \item \textbf{Learning outcomes}:
  \begin{itemize}
  \item run interactive jobs with salloc, a batch job with sbatch
  \item explain the architecture of SLURM, i.e., the role of slurmd, srun and the injection of environment variables
  \item explain the function of the tools: sacct, sbatch, salloc, srun, scancel, squeue, sinfo
  \item explain time limits and the benefit of a backfill scheduler
  \item comprehend that environment variables are set when running a job
  \item comprehend and describe the expected behavior of a simple job scripts
  \item comprehend how variables are prioritized when using command line and a script
  \item change a provided job template and embed them into shell scripts to run a variety of parallel applications
  \item analyze the output generated from submitting to the job scheduler and typically generated errors
  \end{itemize}
\end{itemize}

@@

Secondly, a text file is given to the user that provides the same information.
It is PGP signed using the private key of the HPC Certification Forum to allow verification with the published public key.
It also contains a verification URL that can be given to a third-party allowing verification of the information.

@@

\begin{figure}
  \includegraphics[width=0.48\textwidth]{JulianMKunkel}
  \caption{Draft for an awarded certificate}
  \label{fig:awardedCertificate}
\end{figure}

@@

Firstly, an author of training material is allowed to indicate on the training material itself or on promotional material the fact
which skills are covered by the material completely or partially.
We provide a seal that can be used for that purpose (see \Cref{fig:seal-teaching}).
The reference to the HPCCF and the seal can be used free of charge under the condition that the developer of the training material
registers a link to the material or course and their email address on our webpage using an online form.
That way, the HPCCF is informed about the usage of the seal.

@@

\subsection{Navigation}
%\paragraph{Navigation}
Thanks to the contributions of the PeCoH project, a JavaScript prototype enables the embedding of a navigable skill tree into a webpage.
The script can be used by different stackholders to present their own view on the skill-tree.
By view we mean the selection and organization of the skills, and the additional information provided when navigating the tree.
For instance, you could have a tree for a specific scientific domain, for a specific data center, or even for the role of the tester of a specific application; it could indicate which skills are mandatory or beneficial for these use cases, providing links to training material or adding further supplementary information.

@@

Increase sharing of teaching materials
Documentation of taught skills simplified
Identify missing teaching activities
Tailor skill-tree specifically to users
Correlate lack of skills with efficient us

>>>>

\newcommand{\jk}[1]{\todo[inline]{TODO: #1}}
\newcommand{\ag}[1]{\todo[inline]{IDEA: #1}}
\newcommand{\kh}[1]{\todo[inline]{KH: #1}}

@@

The article is structured as follows:
First, we introduce the HPC Certification Forum and the program in \Cref{sec:forum}.
Then, an overview of the status is given in \Cref{sec:status}.
Next, the organization of competences is discussed in \Cref{sec:skills}.
This leads to the prototypical approach for the certification process in \Cref{sec:certification}.
In \Cref{sec:ecosystem} there\kh{Vorschlag: ohne there} the ecosystem is described.
Related work is presented in \Cref{sec:related}.
Finally, the article is concluded in \Cref{sec:conclusion}.

@@

The forum is organized using a Webpage\footnote{http://hpc-certification.org} and utilizes Slack\kh{Vorschlag: kurzen Hinweis zu Slack ergänzen "...  cloud-based set of proprietary team collaboration tools ..." bzw. Link auf die Website} for communication and monthly meetings.
Members are organized in different roles:
Anyone can become an associate member in the HPCCF free of charge -- e.g., observing the status, being listed on the webpage.
Full members must actively contribute to the program to some extent and have voting rights for the roles of the steering board.
The steering board directs the overall activities and is organized in different responsibilities, i.e., into topic-specific chairs.

@@

\paragraph{Management}
At ISC-HPC 2018, the first steering board had been elected.
We established communication channels via webpage, email and Slack for regular discussion.
Slack is also used to conduct our monthly open meetings between members and the steering board.
At beginning we used video conferencing tools, but found that the chat provides a more inclusive discussion and the asynchronous nature is more productive.
We also established relations with various stackholders involved in HPC education growing the participation in the forum.
Meeting notes with action items are extracted from Slack and documented using Google Doc\kh{Vorschlag: kurze Info zum Tool bzw. Link (wie bei Slack) ergänzen}.

Note that until now contributions of members are voluntarily and follow the schedule as agreed between the contributor and the HPCCF board.
We manage the prospect contributions in a Trello board\kh{Vorschlag: kurze Info zum Tool bzw. Link (wie bei Slack und Google Doc) ergänzen (Trello kennt ja nicht unbedingt jeder Leser); der Begriff "collaborative" sollte irgendwo untergebracht werden}; each member can manage its own card.

\paragraph{Technical}\kh{"Management" (oberhalb) finde ich auf der Ebene alleinstehend gut, "Technical" etwas zu kurz, Vorschlag: "Technical Tasks" (o.ä.)}
According to our goals, we address 1) the definition of competences; 2) the creation of certificates; 3) the examination of practitioners; and 4) an ecosystem of tools supporting them.

@@

A skill is defined as a set of competences (learning outcomes) and some metadata.
This model can be compared to the classification of school knowledge, for example, the skill with the short name “addition” could describe the math skill of being able to add numbers successfully.\kh{ich halte ein prägnantes und gutes Beispiel hier für wichtig. Ohne den Übergang zum Expert Level gefällt mir die "Addition" auch gut, aber der Übergang zu "Expert" mit dem Addieren mehrerer Zahlen ist zwar auf abstrakter Ebene ok, aber doch etwas weit entfernt von der Praxis; so spontan fällt mir als analoges alternatives Beispiel aus dem Bereich der Geometrie das Zeichnen einer Geraden mit dem Lineal ("Basic Level") oder die Konstruktion eines Sechsecks mit Zirkel und Lineal ("Expert Level") ein}.
Within a single skill, there can also be multiple levels (basic, intermediate, expert level) building upon each other that distinguish the expertise further.
We expect that practitioners acquire the lower levels before progressing to more complex levels.
In our addition example, \textit{basic level}, for example, may mean to be able to add two positive numbers while the \textit{expert level} of that skill could indicate to be able to add multiple numbers.

@@

On the leaf level, a skill is fine-grained and orthogonal to other skills -- we scope the level of detail here to be able to be taught in a 1.5 hour lecture up to a 4 hour workshop.
We believe this is a good granularity as it allows practitioners to cherry-pick the relevant skills and lecturers and examiners to prepare small lectures with well-defined content.
\ag{change sentence because provided that provide - \\
Instead: For technology-dependent skills on leaf level (e.g., a specific file system or workload manager), often introductory skills are provided that provide the foundation to many specialized skills each representing a specific hardware or software technology.\\
write it this way: For technology-dependent skills on leaf level (e.g., a specific file system or workload manager), often introductory skills are provided that contribute to the foundation of many specialized skills each representing a specific hardware or software technology.
}
The aggregation within the tree is similar to the aggregation found in education as part of “individual teaching events”, “those specified for modules or short courses”, and “those specified for whole degree programmes” \cite{hussey2008learning}.
While that Hussey et al. conclude that LOs on the coarse grained level are not useful for high-level education, we use a similar concept, but relax the granularity/abstraction level of the learning outcome.\kh{den Satz habe ich nicht genau verstanden; als Leser würde ich mir die Kurzbegründung wünschen, die Hussey et al. für ihre Feststellung anführen}

@@

The following skill describes a leaf-level skill for the usage of SLURM in\kh{at} the basic level.
While there is no formal dependency to the introduction (skill USE4.2.2-B), it is expected that practitioners have obtained the other skill before learning this one.

\begin{itemize}
  \item \textbf{ID}: USE4.2.2-B
  \item \textbf{Name}: SLURM Workload manager
  \item \textbf{Background}: SLURM is a widely used open-source workload manager providing various advanced features\kh{Vorschlag: einige der Highlights anführen: "... , like ..."}.
  \item \textbf{Aims}:
  \begin{itemize}
    \item To enable practitioners to use relevant tools to run and monitor parallel applications using SLURM.
    \item To enable practitioners to comprehend and describe the basic architecture of SLURM and the suite of tools.
  \end{itemize}
  \item \textbf{Learning outcomes}:
  \begin{itemize}
  \item run interactive jobs with salloc, a batch job with sbatch
  \item explain the architecture of SLURM, i.e., the role of slurmd\kh{slurmd haben wir beim "Basic Level" bisher nicht vorgesehen}, srun and the injection of environment variables
  \item explain the function of the tools: sacct, sbatch, salloc, srun, scancel, squeue, sinfo
  \item explain time limits and the benefit of a backfill scheduler
  \item comprehend that environment variables are set when running a job
  \item comprehend and describe the expected behavior of a simple job scripts\kh{typo?}
  \item comprehend how variables are prioritized when using command line and a script
  \item change a provided job template and embed them into shell scripts to run a variety of parallel applications
  \item analyze the output generated from submitting to the job scheduler and typically generated errors
  \end{itemize}
\end{itemize}

@@

Secondly, a text file is given to the user that provides the same information.
It is PGP signed using the private key of the HPC Certification Forum to allow verification with the published\kh{"published" wäre redundant} public key.
It also contains a verification URL that can be given to a third-party allowing verification of the information.

@@

\begin{figure}
  \includegraphics[width=0.48\textwidth]{JulianMKunkel}
  \caption{Draft for an awarded certificate}
  \label{fig:awardedCertificate}
\end{figure}
\kh{Vorschlag: "The basic certificate" ist ja sehr generisch und verlangt vom Leser (vermeidbares) Abstraktionsvermögen; ein prägnantes und praxsinahes Beispiel erscheint mir hier geeigneter}

@@

Firstly, an author of training material is allowed to indicate on the training material itself or on promotional material the fact
which skills are covered by the material completely or partially.
We provide a seal that can be used for that purpose (see \Cref{fig:seal-teaching}).
The reference to the HPCCF and the seal can be used free of charge under the condition that the developer of the training material
registers a link to the material or course and their\kh{Plural hier beabsichtigt (Bezug?)} email address on our webpage using an online form.
That way, the HPCCF is informed about the usage of the seal.

@@

\subsection{Navigation}\kh{Vorschlag Unterkapitel in "Results" umbenennen oder an anderer Stelle aus "Erwartungsgründen" ein "Results"-Kapitel ergänzen (am besten natürlich auf der Hauptgliederungsebene, aber das wird vermutlich schwierig werden)}
%\paragraph{Navigation}
Thanks to the contributions of the PeCoH project, a JavaScript prototype enables the embedding of a navigable skill tree into a webpage.
The script can be used by different stackholders to present their own view on the skill-tree.
By view we mean the selection and organization of the skills, and the additional information provided when navigating the tree.
For instance, you could have a tree for a specific scientific domain, for a specific data center, or even for the role of the tester of a specific application; it could indicate which skills are mandatory or beneficial for these use cases, providing links to training material or adding further supplementary information.

@@

Increase sharing of teaching materials
Documentation of taught skills simplified
Identify missing teaching activities
Tailor skill-tree specifically to users
Correlate lack of skills with efficient us\kh{diese Subsection ist vermutlich noch in Arbeit; Groß-/ Kleinschreibung?}
